### 2020-11-27 paper/sections/introduction.tex
update introduction and using a new figure2

For the collected video, the classical computer vision and deep neural network technology are generally used for video analytics. A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector. Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}). A combination of the knob values is a video analytics \emph{configuration}. The configuration space grows \emph{exponentially} with the number of knobs and their values \cite{jiang2018chameleon}. Since video analytics applications demand intensive computation resources and high accuracy, we pay much attention to the consumption of resources in the calculation process and the accuracy of inference. Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}.

Apparently, choosing different configurations will affect resource consumption and accuracy. When at a fixed frame rate, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources. Similarly, when using the same model with the same resolution, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy. Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy. And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout whole video. This can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.

>>>>

%For the collected video, the classical computer vision and deep neural network technology are generally used for video analytics.

A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector. Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}). A combination of the knob values is a video analytics \emph{configuration}. The configuration space grows \emph{exponentially} with the number of knobs and their values \cite{jiang2018chameleon}. Since video analytics applications demand intensive computation resources and high accuracy, we pay much attention to the consumption of resources in the calculation process and the accuracy of inference. Therefore, the problem that follows is how to balance \emph{resource consumption} and \emph{accuracy}. Different configurations directly affect accuracy and resource consumption. Using a fixed static high configuration can be very precise, but it can also be a huge drain on resource consumption. Similarly, specifying a low configuration will result in a significant reduction in accuracy.

%Apparently, choosing different configurations will affect resource consumption and accuracy. When at a fixed frame rate, using a complex model with high resolution can obviously and accurately detect the target object, but it also requires more computing resources. Similarly, when using the same model with the same resolution, choosing a lower resolution can reduce the computing resources, and the subsequent cost is the decline of accuracy. Obviously, when the target car (object) is large, a smaller model and a lower resolution can meet the accuracy with a large reduction of resource consumption, while the target car (object) is small, a more complex model and higher resolution are needed to achieve a satisfactory accuracy. And in the case of a highway video analytics, due to the rate of car travel cannot be predicted in advance, so when the car drives slowly (or static) because of the traffic jam, we can choose a lower frame rate (such as 1 FPS) instead of having to use a constant high frame rate throughout whole video. This can significantly reduce resource consumption, but does not affect the accuracy of the video analytics.
